---
title: "R Notebook"
author: andyt
date: 5/13/2020
output: html_notebook
---

The [R plugin](https://www.jetbrains.com/help/pycharm/r-plugin-support.html) for IntelliJ-based IDEs provides
handy capabilities to work with the [R Markdown](https://www.jetbrains.com/help/pycharm/r-markdown.html) files.
To [add](https://www.jetbrains.com/help/pycharm/r-markdown.html#add-code-chunk) a new R chunk,
position the caret at any line or the code chunk, then click "+".

The code chunk appears:
```{r}
```

Type any R code in the chunk, for example:
```{r}
mycars <- within(mtcars, { cyl <- ordered(cyl) })
mycars
```

Now, click the **Run** button on the chunk toolbar to [execute](https://www.jetbrains.com/help/pycharm/r-markdown.html#run-r-code) the chunk code. The result should be placed under the chunk.
Click the **Knit and Open Document** to built and preview an output.

  public static int it_partition( Data dataSet, Pivot pivot ){


    //    int a, b;
    //    int pivot = runnable(dataSet,a, b)
    //todo need to return pivot method.
    //    boolean unsorted = true;
    int pivotValue, start = 0, end=dataSet.getSize()-1;
    //call pivot method and get the pivot.

    int pivotIndex = pivot.getPivot( );
    pivotValue = dataSet.getValue( pivotIndex )


//    Integer[] dataSet = records.getData();
    quicksort: while(true){

      //move the lower pointer while its less than 'pivot';
//      while(dataSet[start] < pivotValue){
      while(dataSet.getValue( start )< pivotValue){
        start += 1;
      }

      //move the upper pointer while its more than 'pivot';
//      while(pivotValue < dataSet[end]){
      while(pivotValue < dataSet.getValue(end){
        end -= 1;
      }

      //if 1 or 0 elements remain, then all the numbers are partioned.
      //return 'end'
      if(start >=  end) break quicksort;
        //the pointers have met or crossed.
      else{
        dataSet.swap( start , end );

//        int temp = dataSet[ start ];
//        dataSet[ start ] = dataSet[ end ];
//        dataSet[ end ] = temp;
                      start += 1;
                      end -= 1;
      }
    }
    return end;
  }